%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Manager, Responsible Sourcing} % Job title
    {UPM-Kymmene Oyj} % Organization
    {Helsinki \& Tampere, Finland} % Location
    {Nov. 2010 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % POSITION
        \item {\underline{Manager, Responsible Sourcing} Jan. 2023 - Current}
        \begin{itemize}
            \item {Leading the development of a sustainable sourcing strategy across the supply chain. Ensuring that suppliers meet environmental, social, and governance (ESG) standards, supporting compliance with evolving regulations and company policies. Collaborating with internal and external stakeholders to identify risks, perform mitigation actions (onsite audits \& evaluations) and ensure continuous improvement.}
        \end{itemize}
        % POSITION
        \item {\underline{Senior Specialist, Supplier Quality and Sustainability} Jan. 2021 - Dec. 2022}
        \begin{itemize}
            \item {Ensured sustainable supply chains by organizing online corporate social responsibility assessments for suppliers as well as onsite audits. Together with internal stakeholders, drove suppliers to needed improvements. Participated in the Together for Sustainability initiative as Co-chair of the working stream focused on supplier assessments (via Ecovadis).}
        \end{itemize}
        % POSITION
        \item {\underline{Senior Specialist, Sourcing Operations} Aug. 2019 - Dec. 2020}
        \begin{itemize}
            \item {Continuously developed the process for supply chain sustainability assessments. Reviewed suppliers' performance on CSR topics. Through trainings and communication ensured that the sustainability program was implemented.}
        \end{itemize}
        % POSITION
        \item {\underline{Senior Sourcing Analyst} Mar. 2016 - Aug. 2019}
        \begin{itemize}
            \item {Worked on projects to increase visibility and accuracy of spend \& savings for Global Sourcing. Supported various stakeholders with cost reporting.}
        \end{itemize}
        % POSITION
        \item {\underline{Sourcing Analyst, Paper Business} Sep. 2014 - Feb. 2016}
        \begin{itemize}
            \item {Prepared monthly cost reporting for Paper business. Participated in the preparation of raw material price forecasts and reporting on variable cost savings.}
        \end{itemize}
        % POSITION
        \item {\underline{Specialist, Risk Assessment} Nov. 2010 - Aug. 2014}
        \begin{itemize}
            \item {Provided services to UPM Business Groups in the areas of credit insurance, risk assessment, operational credit control, and credit risk management reporting.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-chair of Workstream 2 (Supplier Assessments)} % Job title
    {Together for Sustainability AISBL} % Organization
    {Brussels, Belgium} % Location
    {May 2021 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-chaired Workstream 2 in the Together for Sustainability initiative, focusing on developing TfS Assessments through member collaboration and cooperation with Ecovadis. The initiative, through its member companies, strives for sustainable development and supports the principles of the United Nations Global Compact and Responsible Care\textregistered.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Accountant, Accounts Payable} % Job title
    {Wärtsilä Finland Oy} % Organization
    {Vaasa, Finland} % Location
    {Sep. 2008 - Oct. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed purchase invoice processing using SAP. Handled payment requests and supported purchase approvers in using supporting systems.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Auditor} % Job title
    {Grant Thornton} % Organization
    {Athens, Greece} % Location
    {2007 - 2008} % Date(s)
    {
      \begin{cvitems}
        \item {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {General Assistant} % Job title
    {Marti Marmol SL} % Organization
    {Spain} % Location
    {2006 - 2007} % Date(s)
    {
      \begin{cvitems}
        \item {}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant} % Job title
    {Hellenic Telecommunications Organization} % Organization
    {Athens, Greece} % Location
    {2003 - 2004} % Date(s)
    {
      \begin{cvitems}
        \item {}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
