%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {MBA International Management \& Trade} % Degree
    {Centre for Economic and Commercial Studies} % Institution
    {Madrid, Spain} % Location
    {Dec. 2009 - Jun. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Intensive 7-month, 600-hour MBA covering law, economics, investments, accounting, logistics, marketing, strategy, and project management. Awarded through a highly selective process, it serves as the entry point to a prestigious programme for young professionals in Spain.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Master In International Business} % Degree
    {University of Vaasa} % Institution
    {Vaasa, Finland} % Location
    {Oct. 2000 - Sep. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {International two-year English programme emphasizing strategic management, marketing, and HR. Completed a Master’s thesis on Learning in Strategic Supply Networks, examining approaches used by large multinational enterprises.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Licenciate In Business Management And Administration} % Degree
    {University of León} % Institution
    {León, Spain} % Location
    {Oct. 2000 - Sep. 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Licenciate programme in Management and Administration, with a strong foundation in micro- and macroeconomics, statistics, econometrics, and financial studies. Completed one academic year as an Erasmus exchange student at the University of Vaasa, Finland.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
