%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {Twoday \emph{- formerly Kaito}} % Organization
    {Helsinki, Finland} % Location
    {Jan. 2022 - Current} % Date(s)
    {   
    \begin{cvitems} % Description(s) of tasks/responsibilities
      % CUSTOMER
      \item {\underline{Data \& Platform Engineer at Metso} Jun. 2023 - Current}
      \begin{itemize}
          \item {Deployed and managed Metso's brand new data platform based on Azure, Snowflake, and dbt, via Terraform; overseeing >2,800 resources, and ensuring consistent development pipelines, streamlined governance, and scalable, reliable operations. This included the initial migration of data from an existing platform based on Databricks.}
          \item {Implemented end-to-end data ingestion from diverse sources—relational databases, Kafka streams, and REST APIs—into Snowflake, leveraging Snowpipe, external stages, and Snowpark Python code deployed as UDFs/UDTFs.}
          \item {Configured and deployed Docker-based services to Azure Container Apps via GitHub Actions and Terraform, enabling repeatable, zero-downtime releases for Kafka Connect, Grafana, Apache Superset, and custom data-integration services.}
          \item {dbt development work.}
      \end{itemize}
      % CUSTOMER
      \item {\underline{Platform Engineer at Ramirent} Mar. 2023 - Jun. 2023}
      \begin{itemize}
          \item {Deployed the foundations of Ramirent's brand new data platform based on Azure, Snowflake, and dbt, with all resources managed via Terraform and orchestrated via Azure DevOps pipelines.}
      \end{itemize}
      % CUSTOMER
      \item {\underline{Platform Engineer at Kaito Insight Oy} Feb. 2023 - Aug. 2024}
      \begin{itemize}
          \item {Refactored Kaito's Terraform product-offering code into a modular and scalable architecture, improving the product's profitability by making it faster deploy, as well as easier to manage, govern, and onboard team members.}
      \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Head Of Solution Design} % Job title
    {Qvantel} % Organization
    {Helsinki, Finland} % Location
    {Apr. 2017 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % POSITION
        \item {\underline{Head Of Solution Design} Jun. 2022 - Dec. 2022.}
        \begin{itemize}
            \item {Manage a geographically distributed team of experts across multiple domains and report directly to the Chief Product Officer; align team efforts to support R\&D, product development, integrations, deliveries, operations, and sales; and handle responsibilities such as project management, R\&D, and analysis of new product requirements.}
        \end{itemize}
        % POSITION
        \item {\underline{Business Intelligence Specialist} Apr. 2018 - Jun. 2022}
        \begin{itemize}
            \item {Engineered end-to-end real-time analytics solutions using Kafka and AWS, including infrastructure-as-code with Terraform and automated deployments via Jenkins; developed Python ETL ingestion functions on AWS Lambda streaming data to RDS; served as Tableau and QuickSight superuser creating and maintaining custom SQL queries, data sources, analyses, and dashboards; and built front-end components in JavaScript with React.}
        \end{itemize}
        % POSITION
        \item {\underline{Senior Business Analyst} Apr. 2017 - Apr. 2018}
        \begin{itemize}
            \item {Gathered reporting and analytics requirements and translated them into clear development specifications. Designed and developed JavaScript dashboards and reports to meet business needs. Built and maintained internal reporting solutions in Tableau.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Market Intelligence Analyst} % Job title
    {Iggesund Paperboard / Holmen Group} % Organization
    {Amsterdam, The Netherlands} % Location
    {Sep. 2015 - Feb. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as BI superuser, supporting sales teams and top management through analysis, report creation, KPI dashboards, and ad hoc visualizations..}
        \item {Explored internal and external data using Excel, SQL, and R to provide insights across business functions, from sales to production.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Closing \& Reporting Specialist} % Job title
    {UPM Kymmene} % Organization
    {Tampere, Finland} % Location
    {Dec. 2011 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed financial and cost accounting period-end closing and reporting for the Brazilian, Italian, and Spanish units.}
        \item {Conducted performance analysis using SAP FICO, Hyperion, and Excel-based reports.}
        \item {Contributed to the SAP integration project for the Brazilian unit.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Foreign Trade Specialist} % Job title
    {ICEX - Spanish Institut For Foreign Trade} % Organization
    {Helsinki, Finland} % Location
    {Oct. 2010 - Oct 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consulting services for Spanish firms expanding operations to Finland and Estonia, including market research and feasibility studies.}
        \item {Prepared market and industry reports for the Spanish Embassy in Finland and the Spanish Institute of Foreign Trade.}
        \item {Supported the promotion of Spanish export sectors through trade fairs, industry events, and public initiatives.}
        \item {Entry-level position within the Spanish Institute of Foreign Trade Young Professionals Programme.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Accounts Payable Trainee} % Job title
    {Wärtsilä} % Organization
    {Vaasa, Finland} % Location
    {Apr. 2008 - May 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Purchase invoice validation from external and group units..}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bank Teller, University Job Placement} % Job title
    {Caja España } % Organization
    {León, Spain} % Location
    {Nov. 2006 - Feb 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deposit and withdrawal, validation, and compliance operations.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Head of Solution Design} % Job title
%     {Qvantel} % Organization
%     {Helsinki, Finland} % Location
%     {Jun. 2022 - Jan. 2023} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Manage a team of geographically distributed experts on a wide range of fields - operations, charging system integrations, CICD pipelines, product development...}
%         \item {Align the work of the team to support R&D, product development, integrations, deliveries, operations, and sales.}
%         \item {Ad-hoc tasks ranging from project management and R&D to analysis of new product requirements.}
%         \item {CICD pipelines in Azure DevOps and Github Actions for Terraform and Docker container services.}
%         \item {The position reports to the Chief Product Officer.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
% \cventry
%   {Business Intelligence Specialist} % Job title
%   {Qvantel} % Organization
%   {Helsinki, Finland} % Location
%   {Apr. 2018 - Jun. 2022} % Date(s)
%   {
%     \begin{cvitems} % Description(s) of tasks/responsibilities
%       \item {Terraform platform engineering development of end-to-end real-time analytics solutions based on Kafka and AWS and management of deployments.}
%       \item {Python development of ETL ingestion functions deployed to AWS Lambda streaming data to AWS RDS.}
%       \item {Tableau and AWS Quicksight superuser creating and maintaining SQL queries, data sources, analysis, and dashboards.}
%       \item {Javascript front-end development with React.}
%       \item {Data Engineering - Development of real time data pipelines for analytic purposes based on Kafka and AWS resources}
%       \item {Platform Engineering - Development of Terraform scripts to automate the deployment of AWS resources and configuration of the Jenkins jobs required to deploy them}
%       \item {Python - Development of functions to process real-time data}
%       \item {Business Intelligence - Development of QuickSight dashboards and the SQL queries powering them}
%       \item {Development of real time analytics applications - Reports, dashboards, insights, ML...}
%       \item {DevOps, CD/CI, JIRA, Git & SCRUM}
%       % Previously
%       \item {Tableau superuser - Creation and maintenance of custom analysis and data sources}
%       \item {Python backend and React frontend development for machine learning POCs}
%       \item {Robotframework frontend testing}
%       \item {Data analysis on SQL databases}
%       \item {Data Engineering - Development of real time data pipelines for analytic purposes based on Kafka and AWS resources.}
%     \end{cvitems}
%   }

%---------------------------------------------------------
  % \cventry
  %   {Accounts Payable Trainee} % Job title
  %   {Wärtsilä} % Organization
  %   {Vaasa, Finland} % Location
  %   {Apr. 2008 - May 2009} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item {Data platform development, management, and governance in Terraform of Azure and Snowflake resources (over 2.8K resources and modules).}
    %   \end{cvitems}
    % }

%---------------------------------------------------------
\end{cventries}
